\huge Tor's Usability for Censorship Circumvention

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
cite the table of all participants and order appendixes to be in order of citation.

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

@@

\section{All Participant Times}
\label{all-participant-times}

>>>>

\subsubsection{Active Time} 
We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges} and summarize where they spent their time in Appendix~\ref{all-participant-times}. Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant. The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.

@@

\section{All Participant Times}
\label{all-participant-times}
Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface. These are the raw numbers used to compute values such as the median time spend on each screen.   Participants are grouped by condition. Within each condition, participants are ordered in the order of time to success. For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.

@@
